### 2019-03-30 ms.tex
Edits to add fit p2i in.

$$i_b = \mathrm{PrevInc}(p_b)$$

where $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
$$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$

@@

The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
The linear predictor is composed of an intercept, covariates, a spatial, Gaussian random field and two iid random effects.

$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$

@@

Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate is able to predict prevalences between 0.004 and 0.27. 
This prior encodes our desire to regularise our model and and belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).

@@

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{llll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88}\\
& Senegal  & {\bf 12.41} &  12.81\\
& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
Spatial a & Indonesia & {\bf 14.81} &  16.45\\
& Senegal  & {\bf 12.31} &  30.12\\
& Madagascar & 67.73 &  {\bf 44.05} \vspace{3mm}\\
Spatial b & Indonesia & {\bf 14.77} &  15.02\\
& Senegal  & {\bf 12.39} &  18.75\\
& Madagascar  & 70.72 &  {\bf 61.05}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\begin{table}[t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals.}}
\begin{tabular}{llll}
\hline
{\bf Cross-validation} & {\bf Country}  & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 0.73 &  0.74\\
& Senegal  & 0.76 &  0.73\\
& Madagascar  & 0.78 &  0.78\vspace{1mm}\\
 Spatial a & Indonesia  & {\bf 0.69} &  {\bf 0.54}\\
& Senegal  & 0.83 &  {\bf 0.59}\\
& Madagascar  & {\bf 0.67} &  0.72 \vspace{1mm} \\
Spatial b & Indonesia & 0.74 &  0.70\\
& Senegal  & {\bf 0.90} &  0.73\\
& Madagascar  & {\bf 0.61} &  {\bf 0.69}\\

>>>>

$$i_b = \exp(\alpha)\mathrm{PrevInc}(p_b).$$

Here $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
$$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
$\alpha$ is a parameter to be fitted that adjusts the previously fitted function.

@@

The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
The linear predictor is composed of a global intercept, $b_0$, and a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
The linear predictor also includes covariates, $X$, and a vector of regression coefficients $\beta$.
Finally we include a spatial, Gaussian random field and two iid random effects.

$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$

@@

Finally, we complete the model by setting priors on the parameters $\beta_0, \brta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
The prevalence only intercept was given a wide, zero-mean prior, $b_0 \sim \operatorname{Norm}(0, 4)$. % check
Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate is able to predict prevalences between 0.004 and 0.27. 
This prior encodes our desire to regularise our model and and belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).

@@

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{llll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88}\\
& Senegal  & {\bf 12.41} &  12.81\\
& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
& Senegal  & {\bf 12.39} &  16.56\\
& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
& Senegal  & {\bf 12.31} &  15.91\\
& Madagascar & 67.73 &  {\bf 44.05}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\begin{table}[t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals.}}
\begin{tabular}{llll}
\hline
{\bf Cross-validation} & {\bf Country}  & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 0.73 &  0.74\\
& Senegal  & 0.76 &  0.73\\
& Madagascar  & 0.78 &  0.78\vspace{1mm}\\
 Spatial 1 & Indonesia & 0.74 &  0.68\\
& Senegal  & 0.90 &  0.83\\
& Madagascar  & 0.61 &  0.69\vspace{1mm} \\
 Spatial 2 & Indonesia  & 0.69 &  0.53\\
& Senegal  & 0.83 &  0.73\\
& Madagascar  & 0.67 &  0.72\\
